\LARGE \bf Preparation of Papers for IEEE Sponsored Conferences \& Symposia*

### 2017-06-12 intro.tex
.

We remark that our work focusses on building piecewise relational
models, and is unrelated to work on analyzing dynamical systems that
have piecewise-affine (PWA) vector fields. Techniques to analyze PWA
dynamical systems using bisimulation relations translate the system
into a non-deterministic infinite state transition system that is
required to be an overapproximation of the original system and use
model checking approaches to verify them \cite{asarin2000approximate}.

>>>>

We remark that our work focusses on building piecewise relational
models, and is unrelated to work on analyzing dynamical systems that
have piecewise-affine (PWA) vector fields. Techniques to analyze PWA
dynamical systems using bisimulation relations translate the system
into a non-deterministic infinite state transition system that is
required to be an over-approximation of the original system and use
model checking approaches to verify them \cite{asarin2000approximate}.

### 2017-06-12 scam.tex
.

\inclfig[width=0.95\linewidth]{vdp_abs.pdf}{The discovered
$0.2$-TS abstraction. Red cells are unsafe cells and green cells are
initial cells.}{vdp-abs}
\begin{example}[Van der Pol Oscillator]~\label{ex:vdp}
We now describe $\epsilon$-TS abstraction using the Van der Pol
    oscillator benchmark from~\cite{zutshi2014multiple}. Simulations
    generated using uniformly random samples are shown in
    \figref{vdp-cont}. We want to check the property $P_3$:
    $x_{unsafe}\in[-1,-6.5]$ and $y_{unsafe}\in[-0.7, -5.6]$, given
    the initial set indicated $x0\in[-0.4, -0.4],\; y_0\in[0.4, 0.4]$.
    We consider the $\epsilon$-TS abstraction defined by the
    quantization function $\quant_{0.2}(\x)$. This results in an
    evenly gridded state-space, where each cell is of size $0.2 \times
    0.2$ units.  $\mathsf{ScatterAndSimulate}$ is then used to
    construct $\TSAbstraction{0.2}{\System}$ using $2$ samples per
    cell and a time step of $\Delta = 0.1s$. The complete process
    follows.  The $\epsilon$-TS abstraction thus discovered is shown
    in \figref{vdp-abs}. The red cells are unsafe and green cells are
    initial cells.
\end{example}

@@

% \subsection{Example: Van der Pol Oscillator}
% \todo{Takes 4 iterations}
% \inclfig[width=0.90\linewidth]{vdp_disc_map.pdf}{Refinement of
% $\epsilon$-TS.}{vdp-map}
%
\begin{example}
\inclfig[width=0.90\linewidth]{vdp_disc_map.pdf}{
Abstract trajectories discovered by $\mathsf{ScatterAndSimulate}$. Each
rectangle denotes a cell which is uniquely identified  by the
tuple against it.
%Cells and trajectory segments used by $1$-relational modeling.
}{vdp-abs-paths}

    Going back to the~\exref{vdp}, $\mathsf{ScatterAndSimulate}$ is able to
    find several abstract trajectories as shown
    in~\figref{vdp-abs-paths}. However, typically, the refinement by
    increasing the quantization precision requires $4$ refinement
    iterations and finally finds a concrete counter-example for
    $\epsilon=0.125$.
\end{example}

>>>>

% \inclfig[width=0.95\linewidth]{vdp_cont_traces.pdf}{Van der
% Pol: continuous trajectories. Red and green boxes indicate unsafe and
% initial sets.}{vdp-cont}
\inclfig[width=0.95\linewidth]{vdp_abs.pdf}{The discovered
$0.2$-TS abstraction. Red cells are unsafe cells and green cells are
initial cells.}{vdp-abs}
\begin{example}[Van der Pol Oscillator]~\label{ex:vdp}
We now describe $\epsilon$-TS abstraction using the Van der Pol
    oscillator benchmark from~\cite{zutshi2014multiple}. Simulations
    generated using uniformly random samples are shown in
    \figref{vdp-abs}. We want to check the property $P_3$:
    $x_{unsafe}\in[-1,-6.5]$ and $y_{unsafe}\in[-0.7, -5.6]$, given
    the initial set indicated $x0\in[-0.4, -0.4],\; y_0\in[0.4, 0.4]$.
    We consider the $\epsilon$-TS abstraction defined by the
    quantization function $\quant_{0.2}(\x)$. This results in an
    evenly gridded state-space, where each cell is of size $0.2 \times
    0.2$ units.  $\mathsf{ScatterAndSimulate}$ is then used to
    construct $\TSAbstraction{0.2}{\System}$ using $2$ samples per
    cell and a time step of $\Delta = 0.1s$. The complete process
    follows.  The $\epsilon$-TS abstraction thus discovered is shown
    in \figref{vdp-abs}. The red cells are unsafe and green cells are
    initial cells.
\end{example}

@@

% \subsection{Example: Van der Pol Oscillator}
% \todo{Takes 4 iterations}
% \inclfig[width=0.90\linewidth]{vdp_disc_map.pdf}{Refinement of
% $\epsilon$-TS.}{vdp-map}
%
\begin{example}
\inclfig[width=0.90\linewidth]{vdp_disc_map.pdf}{
Abstract trajectories discovered by $ScatterAndSimulate$. Each
    rectangle denotes a cell which is uniquely identified  by the
    tuple against it.
}{vdp-abs-paths}

Going back to the~\exref{vdp}, $ScatterAndSimulate$ is able to find
    several abstract trajectories as shown in~\figref{vdp-abs-paths}.
    However, typically, the refinement by increasing the quantization
    precision requires $4$ refinement iterations and finally finds a
    concrete counter-example for $\epsilon=0.125$.

\end{example}
